Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo_merged.tex
commit

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

@@

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, whole brain mounting, whole brain imaging, big data, data management, software management, imaging pipeline, high-throughput imaging}

@@

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM). With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, the storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces. The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent. Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community. 
We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of tens of terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

@@

\subsection{Laser unit}		
The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig. \ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator. %which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. 
Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. %The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. 
A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing). After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

%In its simplest form, the fluorescence detection unit of a light-sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. 
Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm). %To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. 
A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. %In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. 
The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view (FOV) in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for the DAQ board which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation). %Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 250ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

@@

\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
\end{equation}

$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light-sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light-sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

\begin{equation}
w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
\end{equation}

where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
The axial FWHM is then given by:

\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
\end{equation}

The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

\begin{equation}
b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
\end{equation}

The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$. An overview of the relevant formulas concerning the optical properties of a light-sheet microscope is given in Table \ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner. The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip. From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14).

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths. The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four while the experimentally determined axial FWHM was 1.6x larger than the theoretically calculated value of $5.13 \micro m$. The discrepancies, most notably in the lateral direction, are likely caused by aberrations introduced by the gel embedding the fluorescent beads.

@@

%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. %The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation. In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.

@@

\subsection{Software organisation}
Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own Murmex component (see supplementary information \ref{sec:murmex}). Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management. Beyond hardware-related software, two additional Murmex components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.

@@

\section{Data Management}
The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$. This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}). However, image stacks are acquired with a 10\% of linear superposition, which is later used for image stitching. This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.

@@

The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition. Thus, although file conversion drastically reduces data size, in the current implementation it is slower than data production. The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.

With a standard image size of $2048\times 2048$ pixels, and $R_{\text{frame}}=44$ Hz, data are produced at a rate $R_{\text{data}}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2\times 10^7$ $\micro\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h. The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h. Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB. This is well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.

>>>>

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{a} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

@@

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, whole brain, data management, software management, imaging pipeline, high-throughput imaging}

@@

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}. With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces. The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent. Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community. 
We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

@@

\subsection{Laser unit}		
The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised, continuous-wave lasers for fluorescence excitation (Fig. \ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator. %which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. 
Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. %The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. 
A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

%In its simplest form, the fluorescence detection unit of a light-sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. 
Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm, working distance 8mm). %To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. 
A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. %In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. 
The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. For instance, setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for the DAQ board which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation). %Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $\approx 1.45$\cite{Costantini}. To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

@@

\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}},
\end{equation}
$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light-sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light-sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

\begin{equation}
w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w},
\end{equation}
where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
The axial FWHM is then given by:

\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0.
\end{equation}
The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

\begin{equation}
b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}.
\end{equation}
The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$ (assuming $\lambda_0 = 0.5 \micro m$). An overview of the relevant formulas concerning the optical properties of a light-sheet microscope is given in Table \ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner. The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip. From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14). The disagreement with the theoretical value of $5.13 \micro m$ is likely attributed to the refractive index mismatch introduced in the excitation arm by the protective coverslip and by the optical path inside a medium with a refractive index different from air, both causing spherical aberrations\cite{Booth2001}.

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths. The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four. The discrepancy is likely caused by higher order aberrations introduced by the gel embedding the fluorescent beads exacerbated by the high NA of our detection objective\cite{Schwertner2004,Schwertner2007}.

@@

%Our microscope management software has been written in LabVIEW (), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. 
An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. %The graphical user interface (GUI) provides intuitive control of the apparatus as well as full personalisation. In general, the instrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.
The Murmex software development kit (see supplementary information \ref{sec:murmex}) was used to operated the software efficiently and synchronously on different computers.

@@

\subsection{Software organisation}
Each hardware component in the microscope (AOTF, galvo scanners, electro-optical modulator, sample stages, camera, lasers) is managed through its own software component (see supplementary information \ref{sec:murmex}). Since the galvo scanners and the electro-optical modulator are not addressed directly, but via analog and digital signals generated by the DAQ board, their software component just sends analog and digital waveforms to an additional intermediate component responsible for DAQ board management. Beyond hardware-related software, two additional software components, the Stack and Tomo components (see below) orchestrate the operation of the entire system.

@@

\section{Data Management}

The volume of an adult mouse brain has been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size amounts to $0.234\times0.234\times2$ $\micro\text{m}^3$. This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}). However, image stacks are acquired with a 10\% of linear superposition, which is later used for image stitching. This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.

@@

The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition. Thus, although file conversion drastically reduces data size, in the current implementation it is slower than data production. The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on the frame rate $R_{\text{frame}}$ and on the image size: $R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}$
where the factor of two takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.

With a standard image size of $2048 \times 2048$ pixels, and $R_{\text{frame}}=50$ Hz, data are produced at a rate $R_{\text{data}}=400$ MB/s $\approx 1.37$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2.3 \times 10^7$ $\micro\text{m}^3/s$ $\approx 0.08$ $\text{cm}^3$/h. The conversion module can empty the SSD with an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.67 TB/h. Imaging sessions should thus be shorter than 16.3 hours: this limits the maximum amount of raw data being acquired continuously to approximately 22.3 TB. This is well above the disk space needed to image the parallelepiped volume encompassing a whole mouse brain. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.
